%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% --------------------------------------------------------
% Tau
% LaTeX Template
% Version 2.4.4 (28/02/2025)
%
% Author: 
% Guillermo Jimenez (memo.notess1@gmail.com)
% 
% License:
% Creative Commons CC BY 4.0
% --------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[9pt,a4paper,twocolumn,twoside]{tau-class/tau}
\usepackage[english]{babel}
% \usepackage{amssymb}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% Bibliography setup
\usepackage[backend=biber,style=ieee]{biblatex}
\addbibresource{references.bib}

%% Spanish babel recomendation
% \usepackage[spanish,es-nodecimaldot,es-noindentfirst]{babel} 

%% Draft watermark
% \usepackage{draftwatermark}

%----------------------------------------------------------
% TITLE
%----------------------------------------------------------

\journalname{Lab Report}
\title{COP290: Rust Lab Report}

%----------------------------------------------------------
% AUTHORS, AFFILIATIONS AND PROFESSOR
%----------------------------------------------------------

\author[a]{Vani Gupta (2023CS10126)}
\author[a]{Arnav Panjla (2023EE10978)}
\author[a]{Basil Labib (2021TT11175)}

%----------------------------------------------------------

\affil[a]{Indian Institute of Technology, Delhi}

\professor{Professor Abhilash Jindal, COP290 TAs}

%----------------------------------------------------------
% FOOTER INFORMATION
%----------------------------------------------------------

\institution{Indian Institute of Technology, Delhi}
\footinfo{\LaTeX\ Lab Report}
\theday{April 24, 2025}
\leadauthor{Gupta et al.}
\course{Creative Commons CC BY 4.0}

%----------------------------------------------------------
% ABSTRACT AND KEYWORDS
%----------------------------------------------------------

\begin{abstract}    
    We added three extensions to the base Rust TUI spreadsheet program, 1) extended functionality such as undo/redo, autofill, etc. to TUI 2) web application to ease usage 3) multi-user, state-consistent CRDT-based WebSocket spreadsheet programme. 
    We will discuss our design decisions, the system architecture for each extension, and the challenges and learnings from this project in this report.
\end{abstract}

%----------------------------------------------------------

\keywords{lab report, rust, spreadsheet, CRDT, webapp, WebSocket}

%----------------------------------------------------------

\begin{document}
		
    \maketitle 
    \thispagestyle{firststyle} 
    \tauabstract 
    % \tableofcontents
    % \linenumbers 
    
%----------------------------------------------------------

\section{Introduction}

    \taustart{W}e proposed a decentralised, state-consistent spreadsheet program. In order to design and build such a complex system, we decomposed it into three checkpoints. We were able to achieve two out of these three checkpoints and one additional checkpoint not included in our proposal. 

    \begin{itemize}
        \item \cmark Browser-based GUI app using client-server architecture
        \item \cmark Centralised state-consistent real-time GUI app using WebSockets and CRDTs
        \item \xmark Decentralised state-consistent real-time GUI app using WebSockets and CRDTs
    \end{itemize}

    In addition, we also extended the base TUI which was not included in our initial proposal.

    \begin{itemize}
        \item \cmark Added undo/redo up to 5 previous steps
        \item \cmark Predict cell values and autofill ranges
        \item \cmark Support for non-integer datatypes like string, float and consistent operations on strings and floats
    \end{itemize}

\section{TUI Extension}

    \input{content/tuiext.tex}
	
\section{Web Application GUI}

    \input{content/webapp.tex}
    
\section{WebSocket and CRDT-based Web Application}

    \input{content/crdtapp}

\section{Demo images}

    \input{content/images}
%----------------------------------------------------------

\printbibliography

\end{document}