\subsection{Frontend Application Architecture}

The frontend is implemented in Rust and compiled to WebAssembly using the Yew framework, offering a dynamic and reactive interface for interacting with the spreadsheet application.

\subsubsection{Frontend Structure}

\begin{itemize}
    \item \textbf{App Component} - The root component responsible for initializing and structuring the application.
    \item \textbf{TableComponent} - Renders the spreadsheet grid including rows, columns, and populated cell data.
    \item \textbf{CellComponent} - Represents each editable spreadsheet cell with live interaction support.
    \item \textbf{RequestForm} - An input area for command and formula execution.
\end{itemize}

\subsubsection{State Management}

\begin{itemize}
    \item \textbf{AppContext} - Global context for managing application-wide state via reducer pattern.
    \item \textbf{AppState} - Contains shared state data, such as the sheet and UI refresh triggers.
    \item \textbf{AppAction} - Defines state-changing actions such as refreshing the view or updating sheet content.
    \item \textbf{Sheet Model} - The internal data structure representing the spreadsheet grid.
\end{itemize}

\subsubsection{Component Features}

\paragraph{TableComponent}
\begin{itemize}
    \item Fetches data dynamically from the backend API.
    \item Renders an Excel-style grid with labeled row and column headers.
    \item Refreshes the view when a state trigger is activated.
\end{itemize}

\paragraph{CellComponent}
\begin{itemize}
    \item Allows direct in-place editing of individual cells.
    \item Submits values on Enter key press.
    \item Manages focus and selection for a seamless editing experience.
    \item Communicates cell updates to the backend via API.
\end{itemize}

\paragraph{RequestForm}
\begin{itemize}
    \item Provides a dedicated field for command or formula input.
    \item Sends asynchronous requests to the server.
    \item Displays responses or errors as formatted feedback.
\end{itemize}

\subsubsection{API Communication}

\begin{itemize}
    \item Uses \texttt{gloo\_net} for performing HTTP requests in the browser.
    \item Serializes and deserializes data using JSON for communication with the server.
    \item Handles different content types and responses from multiple API endpoints.
    \item Provides robust error handling for failed requests and malformed responses.
\end{itemize}

\subsubsection{UI Features}

\begin{itemize}
    \item Clean and modern responsive design.
    \item Clear feedback for loading states and errors.
    \item Well-structured headers for intuitive navigation.
    \item A command center panel for formula input and result display.
\end{itemize}

\subsubsection{Technical Implementation}

\begin{itemize}
    \item Compiled to WebAssembly for high-performance execution in modern browsers.
    \item Uses Yew hooks to manage component lifecycles and reactivity.
    \item Implements event-driven interactions including form submission and input events.
    \item Employs node references for accessing and manipulating DOM nodes.
    \item Provides in-browser logging and error diagnostics through console output.
\end{itemize}

\subsection{Challenges Faced}

Throughout the development of the spreadsheet application, several technical and architectural challenges were encountered:

\begin{itemize}
    \item \textbf{Formula Parsing Complexity} - Implementing a parser capable of handling nested formulas, precedence rules, and cell references required custom logic and rigorous testing.
    
    \item \textbf{Dependency Tracking} - Maintaining a real-time graph for dependent cells and updating them in the correct order posed consistency and performance challenges.
    
    \item \textbf{Asynchronous Communication} - Synchronizing frontend updates with backend state through async HTTP requests introduced potential race conditions and refresh issues.
    
    \item \textbf{Undo/Redo System} - Designing a history stack that captures full application state snapshots while maintaining performance proved non-trivial.
    
    \item \textbf{WebAssembly Limitations} - Debugging and error tracking in Rust-compiled WebAssembly environments required special attention due to limited debugging tools in browsers.
    
    \item \textbf{Frontend-Backend Type Matching} - Ensuring accurate serialization and deserialization of complex types like formulas and expressions required strict JSON schema adherence.
    
    \item \textbf{Thread Safety} - Managing concurrent access to shared state (`Arc<RwLock<...>>`) without introducing deadlocks or inconsistencies needed careful architectural design.
\end{itemize}

\subsection{Future Improvements}

Several areas have been identified where the application can be further enhanced:

\begin{itemize}
    \item \textbf{UI Enhancements} - Add features such as cell coloring, borders, copy-paste, and multi-cell selection for a richer user experience.
    
    \item \textbf{Live Formula Suggestions} - Integrate formula autocomplete and inline documentation similar to Excel for improved usability.
    
    \item \textbf{Performance Optimization} - Introduce diff-based updates instead of full sheet refreshes to reduce backend load and network traffic.
    
    \item \textbf{Cell Format Types} - Enable formatting for numbers, currencies, dates, and percentage representations.
    
    \item \textbf{Persistent Storage} - Integrate a database (e.g., SQLite or PostgreSQL) for saving and loading spreadsheet sessions across sessions or users.
    
    \item \textbf{User Authentication} - Add login/signup support to allow users to manage private spreadsheets and sync across devices.
    
    \item \textbf{Testing Coverage} - Expand unit and integration test coverage, particularly around formula evaluation and graph updates.
    
    \item \textbf{Real-time Collaboration} - Implement WebSocket-based multi-user editing support for real-time collaboration.
\end{itemize}


This frontend architecture combines the performance of WebAssembly with the ergonomics of Rust and the reactivity of Yew, resulting in a fast, maintainable, and user-friendly spreadsheet interface.
